---
title: "AMA Master File Characteristics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, error=FALSE, results='hide'}
## Imports ----
library(tidyverse)
library(here)
source(here("code", "utils.R"))

counts_orig <- readRDS(here("data", "cleaned_ama_counts.RDS"))

## Flag to those who are active ----
counts_df <- counts_orig %>%
  create_active_grp()
```

## Total observations
- From `r min(counts_df$year)` to `r max(counts_df$year)`, there were a total of `r NROW(counts_df)` person-years of observation in the AMA Master File across `r n_distinct(counts_df$me_num)` unique physicians.

## By type of practice
```{r}
counts_df %>% group_by(active_grp) %>% summarize(n_personyears = n(), n_providers = n_distinct(me_num))
```


- Across all years, there are `r sum(counts_df$active_grp == "active", na.rm = TRUE)` person-years of observations classified as "actively practicing" across `r counts_df %>% filter(active_grp == "active") %>% pull(me_num) %>% n_distinct()` unique physicians. 

- Across all years, there are `r sum(counts_df$active_grp == "not_active", na.rm = TRUE)` person-years of observations classified as "non-actively practicing" across `r counts_df %>% filter(active_grp == "not_active") %>% pull(me_num) %>% n_distinct()` unique physicians. 
## Restricting on age 
```{r}
counts_df %>% filter(between(age, 45, 84)) %>% group_by(active_grp) %>% summarize(n_personyears = n(), n_providers = n_distinct(me_num))
```

- Among these years, after restricting to actively-practicing physicians between 45 and 84 years of age, there are `r counts_df %>% filter(active_grp == "active") %>% filter(between(age, 45, 84)) %>% NROW()` person-years of observations classified as "actively practicing" across `r counts_df %>% filter(active_grp == "active") %>% filter(between(age, 45, 84)) %>% pull(me_num) %>% n_distinct()` unique physicians. 

- Among these years, after restricting to non-actively-practicing physicians between 45 and 84 years of age, there are `r counts_df %>% filter(active_grp == "not_active") %>% filter(between(age, 45, 84)) %>% NROW()` person-years of observations classified as "not actively practicing" across `r counts_df %>% filter(active_grp == "not_active") %>% filter(between(age, 45, 84)) %>% pull(me_num) %>% n_distinct()` unique physicians. 
